Design and Implementation of Probabilistic Programming Language Anglican

### 2016-11-27 paper/paper.tex
minor

    ;; Observing samples from the distribution
    (loop [data0 data]
      (when (not-empty data0)
        (let [[x & data1] data0]
          (observe d x))
        (recur data1)))

>>>>

    ;; Observing samples from the distribution
    (loop [data0 data] ;; Initializing data0
      (when (not-empty data0)
        (let [[x & data1] data0] 
          (observe d x)
          (recur data1))))
